Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-14 prop_letter.tex
prop_letter.tex \section{Gleason} Add a comment...
prop_letter.tex \section{Gleason} Updating...

\begin{thm}\label{thm:convex-uncountable}Let 
\begin{equation}
\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.\label{eq:3-value-intervals}
\end{equation}
For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
described in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}=\mathscr{I}_{0}$
or $\mathscr{I}$ contains uncountably many intervals.\end{thm}

@@

\begin{thm}[Empty core for general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
a three-dimensional Hilbert space, there exists a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}

To prove the theorem, we first need to construct a QIVPM, and then
verify that no states consistent with it on all projectors. Given
an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,
let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$ and $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly~\citep{HOSTunpublished},
where $\mathscr{I}_{0}$ is defined in Eq.~(\ref{eq:3-value-intervals}).
\begin{table}
\caption{\label{tab:non-Born-QIVPM}Define a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
on the three-dimensional Hilbert space. The projectors mapping to
the same interval are listed in the column labeled by $P$ and separated
by commas.}

>>>>

\begin{thm}\label{thm:convex-uncountable}Let 
\begin{equation}
\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.
\end{equation}
For any function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
described in Thm.~\ref{thm:iota-statements}, either $\mathscr{I}=\mathscr{I}_{0}$
or $\mathscr{I}$ contains uncountably many intervals.\end{thm}

@@

\begin{thm}[Empty core for general QIVPMs]\label{thm:Non-extensible-of-Gleason's}In
a Hilbert space of dimension~$d$, there exists a convex QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\coreBorn\left(\bar{\mu},\events\right)=\emptyset$.\end{thm}

To prove the theorem, we first need to construct a QIVPM, and then
verify that no states consistent with it on all projectors. Given
an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2},\ldots,\ket{d-1}\right\} $,
let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$ and $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$.
The function~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$ defined
in Table~\ref{tab:non-Born-QIVPM} can be verified as a QIVPM straightforwardly~\citep{HOSTunpublished},
where
\begin{equation}
\mathscr{I}_{0}=\left\{ \necess,\imposs,\unknown\right\} \,.\label{eq:3-value-intervals}
\end{equation}
\begin{table}
\caption{\label{tab:non-Born-QIVPM}Define a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{0}$
on the three-dimensional Hilbert space. The projectors mapping to
the same interval are listed in the column labeled by $P$ and separated
by commas.}
